A scenario for a Planckian standard kilogram

### 2017-10-24 manuscript_gravitationalconstant.tex
modified plot of G measurements
Table 1 reduced from 4 to 3 columns

\subsection{Description of new measurement}
Newton's law of gravitation does not only explain why an apple falls down from a tree, it also explains orbits. If one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter in an ellipse described by Kepler's laws. The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$. In this proportionality factor, the gravitational constant $G$ appears.
\begin{equation}\label{eq:kepler3}
P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
\end{equation}
If one can measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
So what we need is a freely falling two-body system. The only way to achieve this over some time, is to go to space. Thus, one has to design a spacecraft involving a cavity that contains the two masses and a position measurement apparatus. The cavity should shield the two-body system from environmental influences. The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large inertial forces.\\

@@

\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the sun. Since the activity of the sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of radius $r$, we can express the force on the balls as 
\begin{equation}
F = \frac{1}{3} \pi r^2 \sigma_a T^4.
\end{equation}
with
\begin{equation}
\label{eq:a}
\sigma_a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}
\end{equation}
being a constant that follows from Planck's radiation law.
%
%To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law. The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation and with fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
%
%\begin{equation}
%\label{Stefan-Boltzmann}
%p_r = \frac{1}{3} u = \frac{1}{3} a T^4
%\end{equation}
%where the constant $a$ follows from Planck's radiation law and is
%\begin{equation}
%\label{eq:a}
%a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
%\end{equation}
%We have now a direct relation between radiation pressure and the temperature in the cavity. Then we can estimate the force exerted on a ball of radius $r$ by just multiplying the pressure with the area
%\begin{equation}
%F = \frac{1}{3} \pi r^2 a T^4.
%\end{equation}
%
As we can see, this force is highly temperature dependent. In order to minimize this influence, one should deploy a temperature as small as possible in the cavity. In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K. Such a low temperature results in a force on the balls in the order of $10^{-16}$ N. Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\

@@

\begin{table}[h]
	\centering
	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and and also the value which was chosen to generate data.}
	\begin{ruledtabular}
		\begin{tabular}{l c c c}
			% The codes above determine the horizontal alignment in each column.
			% Options are l (left), r (right), c (centered), and p (paragraph).
			% The p option allows an entry to be broken into multiple lines, and
			% therefore requires a width specification, in this case 5 centimeters.
			Parameter & min. value & max. value & chosen value \\
			\hline	% horizontal line to separate headings from data
			$k$ & $8.0052 \cdot 10^{-10}$ & $8.0112 \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
			$\omega_x$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
			$\omega_y$ & $-1.0 \cdot 10^{-8}$ & $-1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
			$\omega_z$ & $1.95 \cdot 10^{-7}$ & $2.05 \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
			$C_{xx}$ & 0 & $5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
			$C_{yy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{zz}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
			$C_{xy} = C_{yx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{yz} = C_{zy}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
			$C_{xz} = C_{zx}$ & $-1.0 \cdot 10^{-14}$ & $1.0 \cdot 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
			$x_0$ & $0.15$ & $0.1499999$ & $0.1500001$ \\
			$y_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$z_0$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$v_{x_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\ 
			$v_{y_0}$ & $7.30 \cdot 10^{-7}$ & $7.31 \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
			$v_{z_0}$ & $-1.0 \cdot 10^{-7}$ & $1.0 \cdot 10^{-7}$ & $0.0$ \\
		\end{tabular}
	\end{ruledtabular}
	\label{tab:parameters}
\end{table}

>>>>

\subsection{Description of new measurement}
Newton's law of gravitation does not only explain why an apple falls down from a tree, it also explains orbits. If one has two bodies of masses $m_1$ and $m_2$, on which the only force acting is their respective gravitational attraction, they will orbit around their common barycenter in an ellipse described by Kepler's laws. The third law, given in Eq.~(\ref{eq:kepler3}), states that the square of the orbital period $P$ is directly proportional to the cube of the semimajor axis $a$. In this proportionality factor, the gravitational constant $G$ appears.
\begin{equation}\label{eq:kepler3}
P^2 = \frac{4 \, \pi^2}{G(m_1+m_2)}a^3
\end{equation}
If one can measure the position of the two masses very accurately and thus knows the orbit, it is possible to deduce the gravitational constant. 
So what we need is a freely falling two-body system. The only way to achieve this over some time, is to go to space. Thus, one has to design a spacecraft involving a cavity that contains the two masses and a position measurement apparatus. The cavity should shield the two-body system from environmental influences. The spacecraft is then put in space, preferably to a Lagrange point of the earth-sun system, in order to prevent large tidal forces.\\

@@

\textbf{Radiation pressure:} The envelope of the cavity needs to protect the two body-system from the constant bombardment of radiation and charged particles from the sun. Since the activity of the sun varies much, the spacecraft must be able to correct its position around the freely falling masses inside the cavity.\\
Furthermore, there is thermal radiation inside the cavity, that could disturb the orbit.
Using the Stefan-Boltzmann law, we can relate radiation pressure to the temperature inside the cavity. If we then specify to balls of radius $r$, we can express the force on the balls as 
\begin{equation}
F = \frac{8 \pi^6 r^2 {k_\mathrm{B}}^4 T^4}{45 c^3 h^3}.
\end{equation}
%
%To estimate the force on a ball exerted by radiation, we use the Stefan-Boltzmann law. The radiation pressure $p_r$ can be written as a third of the energy density of the electromagnetic radiation and with fundamental thermodynamics one can relate the radiation pressure to the temperature $T$
%
%\begin{equation}
%\label{Stefan-Boltzmann}
%p_r = \frac{1}{3} u = \frac{1}{3} a T^4
%\end{equation}
%where the constant $a$ follows from Planck's radiation law and is
%\begin{equation}
%\label{eq:a}
%a = \frac{8 \pi^5 {k_\mathrm{B}}^4}{15 c^3 h^3}.
%\end{equation}
%We have now a direct relation between radiation pressure and the temperature in the cavity. Then we can estimate the force exerted on a ball of radius $r$ by just multiplying the pressure with the area
%\begin{equation}
%F = \frac{1}{3} \pi r^2 a T^4.
%\end{equation}
%
As we can see, this force is highly temperature dependent. In order to minimize this influence, one should deploy a temperature as small as possible in the cavity. In fact, if a cooling system based on liquid helium is installed, temperature can be brought down to about 4 K. Such a low temperature results in a force on the balls in the order of $10^{-16}$ N. Compared to the gravitational force, this is orders of magnitude less and thus we don't have to worry about effects of radiation pressure.\\

@@

\begin{table}[h]
	\centering
	\caption{This table shows the ranges in which the parameters numerical values in SI units are estimated to make sense and the value which was chosen to generate data.}
	\begin{ruledtabular}
		\begin{tabular}{l c c}
			% The codes above determine the horizontal alignment in each column.
			% Options are l (left), r (right), c (centered), and p (paragraph).
			% The p option allows an entry to be broken into multiple lines, and
			% therefore requires a width specification, in this case 5 centimeters.
			parameter & range & chosen value \\
			\hline	% horizontal line to separate headings from data
			$k$ & $(8.0052$--$8.0112) \cdot 10^{-10}$ & $8.0088 \cdot 10^{-10}$ \\
			$\omega_x$ & $\pm 1.0 \cdot 10^{-8}$ & $0.02 \cdot 10^{-8}$ \\
			$\omega_y$ & $\pm 1.0 \cdot 10^{-8}$ & $-0.03 \cdot 10^{-8}$ \\
			$\omega_z$ & $(1.95$--$2.05) \cdot 10^{-7}$ & $1.996 \cdot 10^{-7}$ \\
			$C_{xx}$ & $0$--$5.0 \cdot 10^{-14}$ & $3.8 \cdot 10^{-14}$ \\
			$C_{yy}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{zz}$ & $\pm 10^{-14}$ & $-0.2 \cdot 10^{-14}$ \\
			$C_{xy} = C_{yx}$ & $\pm 10^{-14}$ & $0.3 \cdot 10^{-14}$ \\
			$C_{yz} = C_{zy}$ & $\pm 10^{-14}$ & $0.1 \cdot 10^{-14}$ \\
			$C_{xz} = C_{zx}$ & $\pm 10^{-14}$ & $-0.4 \cdot 10^{-14}$ \\
			$x_0$ & $0.15 \pm 10^{-7}$ & $0.15$ \\
			$y_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
			$z_0$ & $\pm 10^{-7}$ & $0.0$ \\ 
			$v_{x_0}$ & $\pm 10^{-7}$ & $0.0$ \\ 
			$v_{y_0}$ & ($7.30$--$7.31) \cdot 10^{-7}$ & $7.30698296 \cdot 10^{-5}$ \\
			$v_{z_0}$ & $\pm 10^{-7}$ & $0.0$ \\
		\end{tabular}
	\end{ruledtabular}
	\label{tab:parameters}
\end{table}
